---
title: "Space missions analysis"
output: html_notebook
---

```{r}
price_data <- df %>%
  mutate(
    bin = case_when(
      is.na(Price) ~ NA_character_,
      Price <= 100 ~ "0 - 100",
      Price <= 200 ~ "100-200",
      Price <= 500 ~ "200-500",
      Price <= 1000 ~ "500-1,000",
      Price > 1000 ~ "1,000+",
    )
) %>%
  filter(!is.na(bin)) %>%
  mutate(bin = factor(bin, levels = c("0 - 100", "100-200", "200-500", "500-1,000", "1,000+")))

levels(price_data$bin)

ggplot(price_data, aes(x = bin)) +
  geom_histogram(
    stat = "count",
    color = "black",
    linewidth=0.3,
    fill = "lightskyblue1",
    width=1,
    ) +
  ggtitle("Mission prices") +
  labs(x="Price in millions of USD", y="Count") +
  theme_ipsum()
```
Wrangle the Country Names
You'll need to use a 3 letter country code for each country. You might have to change some country names.

* Russia is the Russian Federation `RUS`
* New Mexico should be `USA`
* Yellow Sea refers to China `CHN`
* Shahrud Missile Test Site should be Iran `IRN`
* Pacific Missile Range Facility should be `USA`
* Barents Sea should be Russian Federation `RUS`
* Gran Canaria should be `USA`

```{r}
#download countries geojson
tmp_geojson <- tempfile(fileext=".geojson")
download.file(
  "https://raw.githubusercontent.com/datasets/geo-countries/cd9e0635901eac20294a57ee3b3ce0684d5e3f1a/data/countries.geojson",
  tmp_geojson
  )
#read contents
library(sf)
countries_sf <- read_sf(tmp_geojson)
```

```{r}
library(countrycode)
library(stringr)
# converting countries into country codes
locations <- df$Location
pattern <- ".*,\\s*(.*)"
countries <- str_match(locations, pattern)[, 2]
subset_countries <- sample(countries, 500)

country_mappings <- c("Russia" = "RUS",
                      "New Mexico" = "USA",
                      "Yellow Sea" = "CHN",
                      "Shahrud Missile Test Site" = "IRN",
                      "Pacific Missile Range Facility" = "USA",
                      "Barents Sea" = "RUS",
                      "Gran Canaria" = "USA")

get_iso3_code <- function(country) {
    if (country %in% names(country_mappings)) {
      return(country_mappings[[country]])
    } else if (grepl("Pacific Ocean", country, ignore.case = TRUE)) {
      return(NA)
    } else {
      iso3_code <- countrycode(country, "country.name", "iso3c")
      #dynamically update country_mappings to run code faster
      country_mappings <<- c(country_mappings, setNames(iso3_code, country))
      return(countrycode(country, "country.name", "iso3c"))
    }
}

iso3_codes <- lapply(countries, get_iso3_code)
print(iso3_codes)

```

```{r}
#add iso3 codes to dataframe
df$iso3_code <- iso3_codes
```

```{r}
# merge countries shapefile with number of successful launches
success_total <- df %>%
  filter(Mission_Status == "Success") %>%
  group_by(ISO_A3) %>%
  summarise(total_successes = n())

countries_sf <- countries_sf %>%
  left_join(success_summary, by = "ISO_A3") %>%
  mutate(total_successes = coalesce(total_successes, 0))

glimpse(countries_sf)
```

```{r}
#plot chloropleth
library(ggplot2)
ggplot(countries_sf) +
  geom_sf(aes(fill = total_successes), linewidth=0.01, alpha=0.9) +
  theme_classic() +
  scale_fill_viridis_c(
    trans = "log", breaks = c(1, 5, 10, 100, 500, 1000),
    name = "Number of successful mission launches",
    guide = guide_legend(
      keyheight = unit(3, units = "mm"),
      keywidth = unit(12, units = "mm"),
      label.position = "bottom",
      title.position = "top",
      nrow = 1
    )
  ) +
  theme(legend.position = "bottom") +
  labs(
    title = "Successful space missions by country")
```
